Delivering Reliable Software in the European Scientific Arena: Evolution of Methodologies and New Trend Analysis

### 2018-01-18 paper-ieee-trans.tex
syntax corrections and rephrasing new trends section

\begin{abstract}
From the advent of Grid technology as the new paradigm of distributed
computing to the current days of Cloud computing models, the continuous need
of new tools and services to match the scientific community requirements has been
addressed in Europe by a various number of projects dedicated to software development
and e-Infrastructure creation, operation and management.
% the creation of software development and e-Infrastructure coordination dedicated projects. 
This work examines the evolution of the software engineering methodologies used in past and
present European Commission-funded projects to illustrate how the research on software
reliability has progressed in Europe over the last 15 years following the foundation of the
first project in 2001. In particular, we will summarize the techniques and procedures
applied to deliver quality software, hightlighting the main challenges and barriers confronted
at the time, and how they were totally or partially overcomed. The base of knowledge collected
throughout these years, sustained by the advances in the area of software engineering,
definitely conformed a significant breakthrough in the reliability of software delivered in the
European research arena. Latest software development projects founded by the European 
Commission are good evidences of such insights, where the enforcement of Quality Assurance
procedures is present since the very early stages of the software development process.
\end{abstract}

@@

\IEEEPARstart{D}uring the last 15 years the provision of an European e-Infrastructure,
that supports an unified access to large-scale computing and intense data analysis
applications, has been driven by the needs of scientific communities as part of their
pan-European research collaborations. One of the well-known examples is the Worldwide 
Large Hadron Collider Computing Grid (WLCG) global computing infrastructure, powered 
by the Particle Physics scientific community, built up to satisfy the computing needs
of processing, storing and analysing the huge quantity of data coming from the Large 
Hadron Collider particle accelerator. A significant number of innovation projects and
technology transfer activities -- embraced by the 5th, 6th and 7th Framework Programmes,
and ultimately by the Horizon 2020 programme \footnote{https://ec.europa.eu/programmes/horizon2020/} -- are being held to coordinate and 
develop distributed solutions that provide a seamless and transparent access to those
computing and data resources, available for the researchers.

@@

>>>>

\begin{abstract}
From the advent of Grid technology -- as the new paradigm of distributed
computing -- to the current days of Cloud computing models, the continuous need
of new tools and services to match the scientific community requirements has been
addressed in Europe by a various number of projects dedicated to software development
and e-Infrastructure creation, operation and management.
% the creation of software development and e-Infrastructure coordination dedicated projects. 
This work examines the evolution of the software engineering methodologies used in past and
present European Commission-funded projects to illustrate how the research on software
reliability has progressed in Europe over the last 15 years following the foundation of the
first project in 2001. In particular, we will summarize the techniques and procedures
applied to deliver quality software, hightlighting the main challenges and barriers confronted
at the time, and how they were totally or partially overcomed. The base of knowledge collected
throughout these years, sustained by the advances in the area of software engineering,
definitely conformed a significant breakthrough in the reliability of software delivered in the
European research arena. Latest software development projects founded by the European 
Commission are good evidences of such insights, where the enforcement of Quality Assurance
procedures is present since the very early stages of the software development process.
\end{abstract}

@@

\IEEEPARstart{D}uring the last 15 years the provision of an European e-Infrastructure,
which supports an unified access to large-scale computing and intense data analysis
applications, has been driven by the needs of scientific communities as part of their
pan-European research collaborations. One of the well-known examples is the Worldwide 
Large Hadron Collider Computing Grid (WLCG) global computing infrastructure, powered 
by the Particle Physics scientific community, built up to satisfy the computing needs
of processing, storing and analysing the huge quantity of data coming from the Large 
Hadron Collider particle accelerator. A significant number of innovation projects and
technology transfer activities -- embraced by the 5th, 6th and 7th Framework Programmes,
and ultimately by the Horizon 2020 programme\footnote{https://ec.europa.eu/programmes/horizon2020/} -- are being held to coordinate and 
develop distributed solutions that provide a seamless and transparent access to those
computing and data resources, available for the researchers.

@@

The INDIGO--DataCloud project is the most recent project in the list and, as such, it is 
the result of the lessons learned from previous experiences in terms of the evaluation and application
of innovative software engineering methodologies, the management of new technologies to put
them into practice, and the compilation and analysis of metrics to measure the success of the
solutions implemented. The expertise gathered is complemented by the fact of being framed in
collaborative projects with an extensive list of partners.

framed projects

All of this with the added complexity of being framed in major
collaborations with

procollecting and analyzing metrics relevant for the .. to empower the sw reliability bla bla bla
